Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-04-13 ltx/BrainIDE.tex
added algorithmx to paper

\usepackage{graphicx}
\usepackage{color}                    % For creating coloured text and background
\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
% TODO environment
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

\author{Dean~R.~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Michael~Dewar}
        Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
        David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
        Anthony~N.~Burkitt,~\IEEEmembership{Member,~IEEE,}
        and~other~Bosses/Supervisors,~\IEEEmembership{Member,~IEEE.}% <-this % stops a space% <-this % stops a space

>>>>

\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}

% \usepackage{graphicx}
\usepackage{color}                    % For creating coloured text and background
\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
% TODO environment
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

\author{Dean~R.~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Michael~Dewar}
        Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
		David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space% <-this % stops a space
